Dissecting Neural Style Transfer

### 2019-06-04 paper/paper.tex
adding the conclusion & related items & inner para contents

The 3nd and 4th dimensions are just spatial locations. 
For a $512\times512$ image they are 512 and 512. 
For intermediate arrays, these 2 dimensions are sometimes scaled down
to half or even $\frac{1}{4}$ of the sizes of the image.

The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
[[[[Not actually necessary to know but insert your elaborations here]]]]

@@

The vanillay neural style transfer algorithm \cite{nst} is 
structured as iteratively solving an optimisation problem.
The argument to optimise is the image as a multidimensional array,
of size $1\times3\times512\times512$ for example.
The interative solver can be many, but in our case it is 
L-BFGS [[[[Maybe elaborate on L-BFGS here]]]]. 
The initial value of the argument could be either white noise or the content image,
but the latter appeared to make the optimisation much easier.

@@

\subsection{Gram matrix}
[[[[Elaborate on gram matrix here]]]]

@@

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy (MMD), which means other Maximum Mean Discrepacies
could be used \cite{MMD}.

[[[[Maybe Describe MMD here]]]]

@@

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then sample statistics or estimators, like (sample) mean, (sample) standard deviation, 
(sample) skewness, (sample) kurtosis and any moments.
Unfortunately, we found that higher moments too slow to compute for our experiments,
so we ended up with the following (combinations) of sample statistics.
\begin{enumerate}
\item Mean and standard deviation of each type of feature. 
That is, given a $1\times64\times256\times256$ feature map, 
we compute an $1\times64\times2$ array.
Standard deviation is favored over variance because standard deviations 
are supposedly of the same unit of measure as the mean, 
while variances are of a squared unit of measure.
\item Mean, standard deviation and 4th central moment to the power of $1/4$. 
That is, a $1\times64\times3$ array for a $1\times64\times256\times256$ feature map.
\item Mean, standard deviation, 4th central moment to the power of $1/4$, 
and 6th central moment to the power of $1/6$.
\end{enumerate}
We have found by experiment that odd-order moments did not work.
6th central moments were already much slower to compute in practice 
than Gram matrices.
So we could only stop at the 6th moment due to limited experimental capacity.

Unfortunately, straight forward histograms were not computationally feasible.
Although the autograd facility could handle histograms in theory, we were not
able to make histograms work in practice. Similarly, sorting or order statistics
like medians were found to be computationally infeasible in practice.

@@

\subsection{Reproducing the original result}
[[[[Fill the experiment part in demo here to show that we have reproduced result.
Cite the original tutorial]]]] \cite{tut}

@@

We will now show that within the general optimisation framework,
steps other than the Gram matrix, 
such as the outputs of which feature maps to derive the style 
losses from are not very essential.

Now let us see something more interesting.

\section{Conclusion and Future Work}

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{MMD}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\bibitem{tut}
Jacq, A. (n.d.). Neural Transfer Using PyTorch (W. Herring, Ed.). Retrieved from https://pytorch.org/tutorials/advanced/neural\_style\_tutorial.html
\end{thebibliography}
\end{document}

>>>>

The 3nd and 4th dimensions are just spatial locations. 
For a $512\times512$ image they are 512 and 512. 
For intermediate arrays, these 2 dimensions are sometimes scaled down
to half or even $\frac{1}{4}$ of the sizes of the image. 
The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.

@@

The vanillay neural style transfer algorithm \cite{nst} is 
structured as iteratively solving an optimisation problem.
The argument to optimise is the image as a multidimensional array,
of size $1\times3\times512\times512$ for example.
The interative solver can be many, but in our case it is 
L-BFGS.It is an optimisation methodology that approximates the BFGS (Broyden - 
Fletcher - Goldfarb - Shanno) algorithm using optimal amount of system 
memory. This algorithm is famous for estimating the parameters in Machine 
Learning domain occupying only linear space for performing the computation. 
The main goal of L-BFGS is to minimize the differentiable scalar function f(x)
over the non-constrained values of  a real valued vector (x).

The initial value of the argument could be either white noise or the content image,
but the latter appeared to make the optimisation much easier.

@@

\subsection{Gram matrix}
Gram matrix is responsible for extracting the style of an image by specifically computing the style loss 
from the style image. For Gram matrix computation, feature vectors are flattened for efficient computation 
that could be easily explained with the help of dot products where more similar the vectors are, lesser the 
angle of difference between them indicating the closer feature relation between image vectors. More angle of 
difference indicates the varied feature image vectors.By computing the dot product of all convolutional 
feature maps with every other feature map yields Gram Matrix which is formulated as,

@@

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy (MMD), which means other Maximum Mean Discrepacies
could be used \cite{MMD}.
Maximum Mean Discrepancy is the spatial probability measure distance that has enormous applications in 
non-parametric testing and machine learning domain. It is defined as the distance between the neighbouring 
mean elements in probability space.

MMDk(P, Q)=||μP * μQ||H Where μ is  the mean in the probability measure space.

@@

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then sample statistics or estimators, like (sample) mean, (sample) standard deviation, 
(sample) skewness, (sample) kurtosis and any moments.
Unfortunately, we found that higher moments are too slow to compute for experiments,
so we ended up with the following (combinations) of sample statistics.
%\begin{enumerate}
%\end{enumerate}

@@

\subsection{Reproducing the original result}

@@

We will also show that other factors, such that the outputs of which functions to derive the style 
losses from are not very essential and somewhat belongs to tuning.

\section{Conclusion}
We have successfully implemented neural style transfer and generated the blende pastiche image
using content image and style image. We have finally concluded that Artistic image is created
with the help of pre-trained CNN. we did use vgg-19 model which is pre-trained model for object 
and face detection and we saw how effectively it was able to detect the texture,and contour of
the image. We determine the content loss by selecting a particular hidden layer’s activation. 
We also determined the style loss with help of Gram Matrix of the hidden layer’s activations.
Total style loss was computed by summing up all the style loss till the layers from where the
content image is selected. Losses were evaluated by using gradient loss dynamically. This was
computed using optimization algorithm of Broyden–Fletcher–Goldfarb–Shanno. This was done by 
inputting the every iteration loss to the network.

\section{Observation}
We found out that we can modify how much style of style image can be inserted in the final image. 
In order to do this, we determined how much content and style of the content image and style image
need to be present. These can be used as hyper parameters to develop the final artistic image. 
More weights of the style of the style image leads to more style and content of the style image
are going to be present in the generated image vice-versa. Another hyper parameter is to choose
the CNN hidden layer activation for the content image. This helps to decide how much content
of content images needs to present in the generated image.

\section{Discussion}
We did find that by putting more weights to style image, more style and content of style images
were getting displayed. By putting in the context, when weights are 105  then content and style
of the content image is lost and style of style image is on the generated image but content of
style image was distorted. In the another process, we did choose different hidden activation layer
in CNN for content image. Ideally, we have selected the middle layer which is ‘CONV_4’. We can
select any of convolution layer to see different result. We found out that by selecting the CONV_1,
the textures of the content image are more prominent. We also found it amazing that after the certain
number of iterations, we are getting blacked out image. It could be possible that losses would have
become zero in this case which further altering the pixel values of the image. However, this is 
something need to be researched Thoroughly.

\section{Lessons Learnt}
We were able to use Pytorch and Tensorflow libraries to implement the image stylization.
We also understood how well CNN model works when image is given as input. We learned to 
compute difference between the two images with the help of content and style. This can be 
computed with the help of gradient loss.

\section {Future Work}
At present, we are applying style of the style image to the whole content image. We are thinking
of using image segmentation technique[1] so to apply style on a particular segment of the image. 
For example, there is a photograph of person wearing a jacket, applying this new technique, 
we would style the jacket with help of some art and apply it back to original image. This means 
old jacket becomes the new one.

\section{Summary of Learning Outcome} 
We learned some crucial concept of programming the project in python using pyTorch and Tensorflow. 
We analysed and evaluated neural style transfer algorithm. We also learned to examined the research
paper and how to link the research paper with other researches to form an innovation solutions. 
We also learned to work in a team. We were able to reflect and use the course learning as our future
work for the neural style transfer.

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{MMD}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}
